Unifying quasars with clumpy wind models

### 2015-08-10 paper.tex
few more tweaks for CK

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/uvspec.png}
\caption
{
Synthetic spectra at four viewing angles in the clumpy model. Plot would look different probably,
and may show composites, but this would be the main synthetic spectrum plot.
}
\label{fig:uvspec}
\end{figure*} %fullpage

@@

Figure 4 shows the synthetic spectrum in the UV from the two models, with the
benchmark model from H13 also shown for comparison. We also show a comparison
to composite quasar and BALQSO spectra in figure 5, with the optical waveband 
included. In the UV, strong BAL profiles are formed in both models. This
highlights the first success of our model: clumping means the correct ionization state 
is maintained in the presence of strong X-rays, allowing large resonance line opacities. 
At the highest inclinations, the 
cooler, lower ionization material at the base of the wind
starts to intersect the line of sight. This produces 
multiple absorption lines lower ionization species such as \mg,
\al\ and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.

@@

To assess the ability of the model to match real 
quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
The model matches the \civ\ and \mg\ line profiles fairly well, 
but the \la\ profile is a factor of $\sim3$ weaker than in the composite spectrum.
This is implies that a larger recombination line formation region is required in order 
to successfully reproduce the strong \la\ emission seen in 
all quasars. We do not produce the semi-forbidden 
intercombination lines seen in quasar spectra because we
currently do not have a treatment for semi-forbidden lines.
This is especially noteiceable with the strong [C~\textsc{iii}~1909\AA\, 
line in the quasar composite spectra.
The critical density of the [C~\textsc{iii}~1909\AA\, line 
is $n_e\sim10^9.5~\rm{cm^{-3}}$, which is higher than much of the 
outer portion of our wind. We therefore expect intercombination lines
to become important coolants in the outer portion of the wind.

>>>>

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/uvspec.png}
\caption
{
Synthetic spectra at five viewing angles in our. The coloured lines
show different quasar and BAL quasar composites, and the dotted line shows a disc
only continuum to show the effect of the outflow on the continuum level.
}
\label{fig:uvspec}
\end{figure*} %fullpage

@@

Figure 4 shows the synthetic spectrum in the UV from our model. 
We also show a comparison
to composite quasar and BALQSO spectra in figure 5.
The UV spectrum is characterised by strong BAL 
profiles at high inclinations ($> 70^\circ$). 
This highlights the first success of our model: 
clumping means the correct ionization state 
is maintained in the presence of strong X-rays, 
allowing large resonance line opacities. 
At the highest inclinations, the 
cooler, lower ionization material at the base of the wind
starts to intersect the line of sight. This produces 
multiple absorption lines lower ionization species such as \mg,
\al\ and Fe~\textsc{ii}, as well as strong Lyman continuum absorption.
The potential links to LoBALQSOs and FeLoBALQSOs are discussed in section 2.4.

@@

To assess the ability of the model to match real 
quasar spectra, we also show {\sl Sloan Digital Sky Survey} (SDSS) quasar composites from
\cite{reichard2003}, normalised to the flux at 2000\AA\ in each panel.
The model matches the \civ\ and \mg\ line profiles fairly well, 
but the \la\ profile is a factor of $\sim2$ weaker than in the composite spectrum.

This is implies that a larger recombination line formation region is required in order 
to successfully reproduce the strong \la\ emission seen in 
all quasars.

We do not produce the semi-forbidden 
intercombination lines seen in quasar spectra because we
currently do not have a treatment for semi-forbidden lines.
This is especially noticable with the strong C~\textsc{iii}]~1909\AA\, 
line in the quasar composite spectra.
The critical density of the C~\textsc{iii}]~1909\AA\, line 
is $n_e\sim10^{9.5}~\rm{cm^{-3}}$, which is higher than much of the 
outer portion of our wind. We therefore expect intercombination lines
to become important coolants in the outer portion of the wind.
